Sufficient Conditions for Reachability in Automata Networks with Priorities

### 2014-03-27 parts/def-ph.tex
simplification section 2

%\todo{Mieux replacer le PH dans un contexte biologique (catalytic networks, metabolic networks)}

@@

\begin{figure}[ht]
  \centering
  \scalebox{1.4}{
  \begin{tikzpicture}
    \TSort{(0,0)}{a}{2}{l}
    \TSort{(0,4)}{b}{2}{l}
    \TSort{(6,2)}{c}{2}{r}

@@

    \path[bounce, bend right]
      \TBounce{ab_3}{}{ab_1}{.north west}
      \TBounce{ab_2}{}{ab_0}{.north west}
      \TBounce{ab_3}{}{ab_2}{.north west}
      \TBounce{ab_1}{}{ab_0}{.north west}
    ;
    \path[bounce, bend left]
      \TBounce{ab_1}{}{ab_3}{.south west}
      \TBounce{ab_0}{}{ab_2}{.south west}
      \TBounce{ab_2}{}{ab_3}{.south west}
      \TBounce{ab_0}{}{ab_1}{.south west}
    ;
    \path[bounce, bend right]
      \TBounce{a_1}{}{a_0}{.north west}
      \TBounce{b_1}{}{b_0}{.north west}
    ;
    \path[bounce, bend left]
      \TBounce{a_0}{}{a_1}{.south west}
      \TBounce{b_0}{}{b_1}{.south west}
    ;
    \path[bounce, bend left]
      \TBounce{c_0}{}{c_1}{.south west}
    ;
    \TState{a_1, b_0, ab_2, c_0}
  \end{tikzpicture}
  }
  \caption{
  \label{fig:ph-livelock}
    An example of PH with $2$ classes of priorities.
    Sorts are represented as labelled boxes and processes as circles with their identifier on the side.
    Actions of $\PHh^{(1)}$ are represented by thick arrows and actions of $\PHh^{(2)}$ are represented by single arrows;
    the hit part of each action in drawn in plain line and the bounce part is in dotted line.
    Greyed processes stand for a possible state $s = \PHstate{a_1, b_0, c_0, ab_{10}}$.
  }
\end{figure}

@@

\todo{Nouvelle section pour les hypothèses + conséquences ?}
\subsection{Restrictions}
\label{ssec:hypothesis}

@@

%\pref{cr:2prio} allows to distinguish two kinds of actions:
%\emph{unprioritised actions} modelling the non-determinacy of biological evolutions
%and \emph{prioritised actions} used to model non-biological behaviours in the model, namely the update of cooperative sorts.
\pref{cr:bounded} states that the dynamics of the studied model $\PH$ contains no infinite sequence of prioritised actions.
As these actions can be considered as non-biological and therefore instantaneous, we thus prevent the existence of any Zeno-like behaviour
which would allow the play of an infinite sequence of prioritised actions in “zero time”.
\todo{Change “Criterion” to something else?}
%\begin{criterion}[2 classes of priorities]
%\label{cr:2prio}
%  In this paper, we only consider Process Hitting with $2$ classes of priorities:
%  $\PH = (\PHs; \PHl; \PHa^{\langle 2 \rangle})$.
%\end{criterion}
%
\begin{criterion}[Bounded termination]
\label{cr:bounded}
  The dynamics of $\restriction{\PH}{1}$ contains no cycles:
  $\exists N \in \sN, \forall s \in \PHl, \forall \delta \in \restriction{\Sce}{1}(s), |\delta| \leq N$.
\end{criterion}

In \pref{def:component} we define a well-formed component as a sort that is hit only by unprioritised actions, or that no action hits.
\begin{definition}[Well-formed component]
\label{def:component}
  A sort $a \in \PHs$ is a \emph{well-formed component} if and only if:
    $\forall h \in \PHh, \PHsort(\PHtarget(h)) = a \Rightarrow \prio(h) \geq 2$ \enspace.
  We denote $\components\subset\Sigma$ the set of well-formed components.
\end{definition}

\pref{def:chainsactions} defines chains of prioritised actions,
and \pref{cr:cyclefreeness} prevents the presence of cycles in these chains.
\begin{definition}
\label{def:chainsactions}
  The set of chains of actions $\PHh(a, b)$ between two sorts $a, b \in \PHs$ is defined as below:
  \begin{align*}
  \PHh(a, b) = \{ (h_i)_{i \in \segm{1}{s+1}} &\in (\PHh^{(1)})^{s+1} \mid s \in \sN \\
    & \wedge \PHsort(\PHhitter(h_1)) = a \wedge \PHsort(\PHtarget(h_{s+1})) = b \\
    & \wedge \forall i \in \segm{1}{s}, \PHsort(\PHtarget(h_{i})) = \PHsort(\PHhitter(h_{i+1})) \}
  \end{align*}
  where $(\PHh^{(1)})^{s+1}$ is the Cartesian product of $s+1$ times the set $\PHh^{(1)}$.
\end{definition}
%
\begin{criterion}[Cycle-freeness in prioritised actions]
\label{cr:cyclefreeness}
  There is no cycles in chains of actions:
  $\forall a \in \PHs, \PHh(a, a) = \emptyset$.
\end{criterion}

In \pref{def:neighbours} we define the notion of neighbouring sorts and actions of a given sort.
The set of neighbouring sorts $\Vs(a)$ of a sort $a$ is the set of components that can interact with it through prioritised actions.
The set of neighbouring actions $\Vh(a)$ of $a$ is the set of prioritised actions influencing $a$.
These definitions are permitted by \pref{cr:cyclefreeness}.
\begin{definition}[$\Vs : \PHs \rightarrow \powerset(\PHsort)$; $\Vh : \PHs \rightarrow \powerset(\PHh)$]
\label{def:neighbours}
  For all sort $a \in \PHs$,
  \begin{align*}
    \Vs(a) &= \{ b \in \components \mid \PHh(b, a) \neq \emptyset \}\\
    \Vh(a) &= \{ h \in \PHh^{(1)} \mid \exists b \in \Vs(a), \exists hs \in \PHh(b,a), h \in hs \}
  \end{align*}
\end{definition}

Finally, we introduce the notion of local steady-state of a sort from a given state.
This local steady-state is the set of processes towards which the sort tends to evolve to, and stay in, when playing only prioritised actions.
We denote $\pfp_s(a)$ this set of processes for a sort $a$ in state $s$ (\pref{def:pfp}),
and we derive from this the notion of well-formed cooperative sort (\pref{def:cs}).
A well-formed cooperative sort models a cooperation between sorts as presented in \pref{ssec:cooperation};
therefore, it must be only hit by prioritised actions,
in a way that its local steady-states efficiently represent all configurations of its neighbouring sorts.
\begin{definition}[$\pfp : \PHl \times \PHs \rightarrow \powerset(\PHproc)$]
\label{def:pfp}
  For all $s \in \PHl$ and $a \in \PHs$,
  \begin{align*}
    \pfp_s(a) = \{ a_i \in \PHl_a &\mid \exists \delta \in \restriction{\Sce}{1}(s), \PHget{(s \PHplay \delta)}{a} = a_i \\
    & \quad \wedge \forall \PHhit{b_i}{c_j}{c_k} \in \Vh(a), \PHget{(s \PHplay \delta)}{b} \neq b_i \vee \PHget{(s \PHplay \delta)}{c} \neq c_j \}
  \end{align*}
  Of course, if $a \in \components$, then $\pfp_s(a) = \{ \PHget{s}{a} \}$.
\end{definition}
%
\begin{definition}[Well-formed cooperative sorts ($\cs$)]
\label{def:cs}
  A sort $a \in \PHs$ is a \emph{well-formed cooperative} sort if and only if:
  \begin{enumerate}[(i)]
    \item $\exists b \in \PHs, \PHh(b, a) \neq \emptyset$
    \item \label{csai} $\forall s \in \PHl, \exists a_i \in \PHl_a, \pfp_s(a) = \{ a_i \}$
    \item \label{css} $\forall a_i \in \PHl_a, \exists s \in \PHl, \pfp_s(a) = \{ a_i \}$
  \end{enumerate}
  We call $\cs$ the set of well-formed cooperative sorts.
\end{definition}

Because of \pref{def:cs}(\ref{csai}), we denote in the following: $\pfp_s(a) = a_i$.
Furthermore, because of \pref{def:cs}(\ref{css}), we denote $\csState(a_i)$ the set of sub-states represented by the process $a_i$ of any cooperative sort $a$ (\pref{def:csState}).
\begin{definition}[$\csState : \PHproc \rightarrow \powerset(\PHproc)$]
\label{def:csState}
  If $a \in \cs$ and $a_i \in \PHl_a$, we define:
  $$\csState(a_i) = \{ ps \in \PHsubl[\PHl]_{\Vs(a)} \mid \forall s \in \PHl, \pfp_{s \Cap ps}(a) = a_i \}$$
%  $$\csState(a_i) = \{ ps \in \underset{b \in \Vs(a)}{\times} \PHl_b \mid \forall s \in \PHl, \pfp_{s \Cap ps}(a) = a_i \}$$
\end{definition}

In the following we simply write “component” (\resp “cooperative sort”) instead of “well-formed component” (\resp “well-formed cooperative sort”).
Finally, \pref{cr:compcs} states that the set of sorts of the considered PH must be divided between components and cooperative sorts.
\begin{criterion}[Components \& cooperative sorts partition]
\label{cr:compcs}
  $$\PHs = \components \cup \cs \wedge \components \cap \cs = \emptyset$$
\end{criterion}

@@

The criteria given in this subsection allow to define a class of PH models that is (weakly) bisimilar to Asynchronous Boolean Networks
or, more generally, to the multivalued version of this framework, called Asynchronous Discrete Networks (ADN).
A translation of ADN into PH and its correction are given in \pref{sec:dn}.

@@

We first denote by $\update(s)$ the state equivalent to $s$ but in which all cooperative sorts are updated (\pref{def:update}).
This state is unique due to the properties of $\pfp$ given in the previous subsection.
Then, \pref{th:update} states that from any state, there exists a scenario updating the cooperative sorts of this state.
%
\begin{definition}[$\update : \PHl \rightarrow \PHl$]
\label{def:update}
  For all $s \in \PHl$, we define:
  \begin{align*}
    \update(s) = s \Cap \{ \pfp_{s}(a) \mid a \in \cs \} \enspace.
  \end{align*}
\todo{Extend to $s \in \PHsubl[\PHl]$ to use it in $\PHflat$?}
\end{definition}
%
\begin{theorem}
\label{th:update}
  $\forall s \in \PHl, \exists \delta \in \restriction{\Sce}{1}(s), s \PHplay \delta = \update(s)$
\end{theorem}
%
\newproof{proofupdate}{Proof of \pref{th:update}}
\begin{proofupdate}
  Let $a$ be a cooperative sort so that $\PHget{s}{a} \neq \pfp_s(a)$.
  Given the definition of $\pfp_s(a)$, there exists a scenario $\delta$ updating $a$ in $s$ so that
  $\forall \delta' \in \restriction{\Sce}{1}(s \PHplay \delta)$, $\PHget{(s \PHplay \delta \PHplay \delta')}{a} = \pfp_s(a)$.
  As there is no cycle of actions between the cooperative sorts (\pref{cr:cyclefreeness}) and given that an updated cooperative sort cannot evolve, at most $|\cs|$ updates have to be performed.
\end{proofupdate}

\pref{th:hcompcomp} states that for a given state $s$, and for any action $h = \PHhit{a_i}{b_j}{b_k}$ where $a$ and $b$ are components,
if $\PHget{s}{a} = a_i$ and $\PHget{s}{b} = b_j$, then
$h$ can always be played after a series of prioritised hits (and these hits do not prevent it to be fired).
\pref{th:hcscomp} states the same if $a$ is a cooperative sort, under the condition that $a$ is updated in $s$.
\begin{theorem}
\label{th:hcompcomp}
  $\forall s \in \PHl, \forall a,b \in \components, \forall h = \PHhit{a_i}{b_j}{b_k} \in \PHh,$\\
  $(\PHget{s}{a} = a_i \wedge \PHget{s}{b} = b_j) \Rightarrow (\exists \delta \in \restriction{\Sce}{1}(s),
  (s \PHplay \delta) \PHPtrans (s \PHplay \delta \PHplay h))$
\end{theorem}
%
\newproof{proofhcompcomp}{Proof of \pref{th:hcompcomp}}
\begin{proofhcompcomp}
  From \pref{th:update}, there exists a scenario $\delta$ with: $(s \PHplay \delta) = \update(s)$.
  As $a,b \in \components$, $a_i \in (s \PHplay \delta)$ and $b_j \in (s \PHplay \delta)$.
  Finally, by definition of $\update(s)$, no prioritised action can be played in $(s \PHplay \delta)$, thus $h$ can be played in $(s \PHplay \delta)$.
\end{proofhcompcomp}
%
\begin{theorem}
\label{th:hcscomp}
  $\forall s \in \PHl, \forall h = \PHhit{a_i}{b_j}{b_k} \in \PHh, a \in \cs, b \in \components,$\\
  $(\PHget{s}{a} = a_i \wedge \PHget{s}{b} = b_j \wedge \pfp_s(a) = a_i) \Rightarrow (\exists \delta \in \restriction{\Sce}{1}(s),
  (s \PHplay \delta) \PHPtrans (s \PHplay \delta \PHplay h))$
\end{theorem}
%
\newproof{proofhcscomp}{Proof of \pref{th:hcscomp}}
\begin{proofhcscomp}
  Similar to the proof of \pref{th:hcompcomp};
  as $a_i \in \pfp_s(a)$, $a_i \in (s \PHplay \delta)$.
\end{proofhcscomp}

>>>>

@@

\begin{figure}[tb]
  \centering
  \scalebox{1.2}{
  \begin{tikzpicture}
    \TSort{(0,0)}{a}{2}{l}
    \TSort{(0,4)}{b}{2}{l}
    \TSort{(6,2)}{c}{2}{r}

@@

    \path[bounce, bend right]
      \TBounce{ab_3}{}{ab_1}{.north west}
      \TBounce{ab_2}{}{ab_0}{.north west}
      \TBounce{ab_3}{}{ab_2}{.north west}
      \TBounce{ab_1}{}{ab_0}{.north west}
    ;
    \path[bounce, bend left]
      \TBounce{ab_1}{}{ab_3}{.south west}
      \TBounce{ab_0}{}{ab_2}{.south west}
      \TBounce{ab_2}{}{ab_3}{.south west}
      \TBounce{ab_0}{}{ab_1}{.south west}
    ;
    \path[bounce, bend right]
      \TBounce{a_1}{}{a_0}{.north west}
      \TBounce{b_1}{}{b_0}{.north west}
    ;
    \path[bounce, bend left]
      \TBounce{a_0}{}{a_1}{.south west}
      \TBounce{b_0}{}{b_1}{.south west}
    ;
    \path[bounce, bend left]
      \TBounce{c_0}{}{c_1}{.south west}
    ;
    \TState{a_1, b_0, ab_2, c_0}
  \end{tikzpicture}
  }
  \caption{
  \label{fig:ph-livelock}
  	\todo{(Loic) mettre la sorte coopérative horizontale pour mieux voir les
	frappes}
    An example of PH with $2$ classes of priorities.
    Sorts are represented as labelled boxes and processes as circles with their identifier on the side.
    Actions of $\PHh^{(1)}$ are represented by thick arrows and actions of $\PHh^{(2)}$ are represented by single arrows;
    the hit part of each action in drawn in plain line and the bounce part is in dotted line.
    Greyed processes stand for a possible state $s = \PHstate{a_1, b_0, c_0, ab_{10}}$.
  }
\end{figure}

@@

\subsection{Restrictions}
\label{ssec:hypothesis}

@@

%\pref{cr:2prio} allows to distinguish two kinds of actions:
%\emph{unprioritised actions} modelling the non-determinacy of biological evolutions
%and \emph{prioritised actions} used to model non-biological behaviours in the model, namely the update of cooperative sorts.
\pref{cr:bounded} states that the dynamics of the studied model $\PH$ contains no infinite sequence of prioritised actions.
As these actions can be considered as non-biological and therefore instantaneous, we thus prevent the existence of any Zeno-like behaviour
which would allow the play of an infinite sequence of prioritised actions in “zero time”.
As a consequence, the set $\restriction{\Sce}{1}$ is finite.
%\begin{condition}[2 classes of priorities]
%\label{cr:2prio}
%  In this paper, we only consider Process Hitting with $2$ classes of priorities:
%  $\PH = (\PHs; \PHl; \PHa^{\langle 2 \rangle})$.
%\end{condition}
%
\begin{condition}[Bounded termination]
\label{cr:bounded}
  The dynamics of $\restriction{\PH}{1}$ contains no cycles:
  $\exists N \in \sN, \forall s \in \PHl, \forall \delta \in \restriction{\Sce}{1}(s), |\delta| \leq N$.
\end{condition}

Given a sort $a\in\Sigma$ and a state $s\in L$, 
we denote $\pfp_s(a)$ (\pref{def:pfp}) the processes of sort $a$ that can be present after
playing all actions of priority $1$,
which is always defined because of \pref{cr:bounded}.

\begin{definition}[$\pfp : \PHl \times \PHs \rightarrow \powerset(\PHproc)$]
\label{def:pfp}
  For all $s \in \PHl$ and $a \in \PHs$,
  \begin{align*}
    \pfp_s(a) = \{ \get{(s\play\delta)}{a} \in \PHl_a &\mid \delta \in \restriction{\Sce}{1}(s)
					\wedge\nexists h\in\PHh^{(1)}, (\delta; h) \in\restriction{\Sce}{1}(s) \}
  \end{align*}
\end{definition}

Our second condition (\pref{cr:compcs}) imposes that any sort in the Process
Hitting is either a well-formed component (\pref{def:component}) or a well-formed cooperative sort
(\pref{def:cs}).
The former is a sort that is hit only by actions with priority greater than $2$.
The latter is a sort that is hit only by actions with priority $1$ and which
always converge to the same process with respect to the state of the components
that have an influence on it (\pref{def:conn}).
We note $\components\subset\Sigma$ the set of well-formed components,
and $\cs\subset\Sigma$ the set of well-formed cooperative sorts.

\begin{definition}[Well-formed component ($\components$)]
\label{def:component}
A sort $a \in \PHs$ is a \emph{well-formed component} if and only if:
    $\forall h \in \PHh, \PHsort(\PHtarget(h)) = a \Rightarrow \prio(h) \geq 2$ \enspace.
\end{definition}

\begin{definition}[Components influence $(\compin: \PHs\to\powerset(\components))$]
\label{def:conn}
Given a sort $a$, $\compin(a)\DEF \conn(a)\cap\components$ where
$\conn(a)$ is the smallest set of sorts satisfying the following properties:
\begin{align*}
a\in\conn(a) &
\\
\forall h\in  \PHh^{(1)},
	\Sigma(\target{h})\in\conn(a) & \Longrightarrow \Sigma(\hitter{h})\in\conn(a)
\end{align*}
\end{definition}

\begin{definition}[Well-formed cooperative sorts ($\cs$)]
\label{def:cs}
A sort $a \in \PHs$ is a \emph{well-formed cooperative} sort if and only if:
\begin{enumerate}[(i)]
\item $\forall h\in\PHh, \Sigma(\PHtarget(h))=a \Longrightarrow \prio(h) = 1$;
\item\label{csai} $\forall s\in\PHl, \card{\pfp_s(a)} = 1$;
\item\label{css} $\forall a_i \in \PHl_a, \exists s \in \PHl, a_i\in\pfp_s(a)$;
\item $\forall \sigma\in\PHsubl[\PHl]_{\compin(a)},
			\forall s,s'\in\PHl,
				\sigma\subseteq s\wedge \sigma\subseteq s'\Rightarrow 
							\pfp_s(a) = \pfp_{s'}(a)$\enspace.
\end{enumerate}
\end{definition}

\begin{condition}[Components \& cooperative sorts partition]
\label{cr:compcs}
  $$\PHs = \components \cup \cs \wedge \components \cap \cs = \emptyset$$
\end{condition}

Because of \pref{def:cs}(\ref{csai}), we denote in the following: $\pfp_s(a) = a_i$.
Furthermore, because of \pref{def:cs}(\ref{css}), we denote $\csState(a_i)$ the set of sub-states represented by the process $a_i$ of any cooperative sort $a$ (\pref{def:csState}).
\begin{definition}[$\csState : \PHproc \rightarrow \powerset(\PHproc)$]
\label{def:csState}
  If $a \in \cs$ and $a_i \in \PHl_a$, 
  $$\csState(a_i) \DEF \{ \toset{ps} \mid ps\in\PHsubl[\PHl]_{\compin(a)} \wedge
  							\exists s\in\PHl, (ps\subset s\wedge \pfp_s(a)=a_i)
							\}$$
\end{definition}

In the following we simply write “component” (\resp “cooperative sort”) instead of “well-formed component” (\resp “well-formed cooperative sort”).

@@

@@

We first denote by $\update(s)$ the state equivalent to $s$ but in which all cooperative sorts are updated (\pref{def:update}).
This state is unique due to the properties of $\pfp$ given in the previous subsection.
Then, \pref{th:update} states that from any state, there exists a scenario updating the cooperative sorts of this state.
%
\begin{definition}[$\update : \PHl \rightarrow \PHl$]
\label{def:update}
  For all $s \in \PHl$, we define:
  \begin{align*}
    \update(s) = s \Cap \{ \pfp_{s}(a) \mid a \in \cs \} \enspace.
  \end{align*}
\end{definition}
%
\begin{theorem}
\label{th:update}
  $\forall s \in \PHl, \exists \delta \in \restriction{\Sce}{1}(s), s \PHplay \delta = \update(s)$
\end{theorem}
%
\begin{proof}
  Let $a$ be a cooperative sort so that $\PHget{s}{a} \neq \pfp_s(a)$.
  Given the definition of $\pfp_s(a)$, there exists a scenario $\delta$ updating $a$ in $s$ so that
  $\forall \delta' \in \restriction{\Sce}{1}(s \PHplay \delta)$, $\PHget{(s \PHplay \delta \PHplay \delta')}{a} = \pfp_s(a)$.
\end{proof}

\pref{th:hcompcomp} states that for a given state $s$, and for any action $h = \PHhit{a_i}{b_j}{b_k}$ where $a$ and $b$ are components,
if $\PHget{s}{a} = a_i$ and $\PHget{s}{b} = b_j$, then
$h$ can always be played after a series of prioritised hits (and these hits do not prevent it to be fired).
\pref{th:hcscomp} states the same if $a$ is a cooperative sort, under the condition that $a$ is updated in $s$.
\begin{theorem}
\label{th:hcompcomp}
  $\forall s \in \PHl, \forall a,b \in \components, \forall h = \PHhit{a_i}{b_j}{b_k} \in \PHh,$\\
  $(\PHget{s}{a} = a_i \wedge \PHget{s}{b} = b_j) \Rightarrow (\exists \delta \in \restriction{\Sce}{1}(s),
  (s \PHplay \delta) \PHPtrans (s \PHplay \delta \PHplay h))$
\end{theorem}
%
\begin{proof}
  From \pref{th:update}, there exists a scenario $\delta$ with: $(s \PHplay \delta) = \update(s)$.
  As $a,b \in \components$, $a_i \in (s \PHplay \delta)$ and $b_j \in (s \PHplay \delta)$.
  Finally, by definition of $\update(s)$, no prioritised action can be played in $(s \PHplay \delta)$, thus $h$ can be played in $(s \PHplay \delta)$.
\end{proof}
%
\begin{theorem}
\label{th:hcscomp}
  $\forall s \in \PHl, \forall h = \PHhit{a_i}{b_j}{b_k} \in \PHh, a \in \cs, b \in \components,$\\
  $(\PHget{s}{a} = a_i \wedge \PHget{s}{b} = b_j \wedge \pfp_s(a) = a_i) \Rightarrow (\exists \delta \in \restriction{\Sce}{1}(s),
  (s \PHplay \delta) \PHPtrans (s \PHplay \delta \PHplay h))$
\end{theorem}
\begin{proof}
  Similar to the proof of \pref{th:hcompcomp};
  as $a_i \in \pfp_s(a)$, $a_i \in (s \PHplay \delta)$.
\end{proof}

### 2014-03-27 parts/sa.tex
simplification section 2

We consider in this section a PH model $\PH = (\PHs; \PHl; \PHa^{\langle 2 \rangle})$ with $2$ classes of priorities
that respects all Criteria (\ref{cr:bounded}, \ref{cr:cyclefreeness} \& \ref{cr:compcs}) of \pref{ssec:hypothesis}.

@@

  However, if $\PHhit{a_0}{b_0}{b_1}$ and $\PHhit{b_0}{a_0}{a_1}$ are replaced by
  $\PHhit{a_0}{a_0}{a_1}$ and $\PHhit{b_0}{b_0}{b_1}$,
  then \pref{th:approxinf} concludes that $c_1$ is reachable from $\ctx$.
\end{example}

\begin{figure}[ht]
  \centering
  \begin{tikzpicture}[aS]
    \node[Aproc] (c1) {$c_1$};
    \node[Aobj,below of=c1] (c01) {$\PHobj{c_0}{c_1}$};
    \node[Asol,below of=c01] (c01s) {};

@@

    (b0) edge (b10) edge (b00)
    (b10) edge (b10s)
    (b00) edge (b00s)
    (b1) edge (b01) edge (b11)
    (b01) edge (b01s)
    (b01s) edge (a0)
    (b11) edge (b11s)
    ;
    \end{tikzpicture}
  \caption{
  \label{fig:sa-livelock}
    The graph of local causality of the PH model in \pref{fig:ph-livelock}.
    Rectangular nodes containing a single process are elements in $\Proc$,
    nodes containing a couple of processes are elements in $\Obj$
    and circle nodes are elements in $\Sol$.
    %The double arrow and the two surrounding nodes represent the only edge in $\Proc \times \Sol$.
    \pref{th:approxinf} is inconclusive on this example as edge $(ab_{11}, \{ a_1, b_1 \}) \in \Proc \times \Sol$ (here represented with a double line) is not coherent (\pref{def:coherent}).
    Indeed, $a_0 \in \Proc$ is a child of $\{ a_1, b_1 \}$, but $a_0 \neq a_1$ (and the same also stands for $b_0$).
  }
\end{figure}

>>>>

We consider in this section a PH model $\PH = (\PHs; \PHl; \PHa^{\langle 2 \rangle})$ with $2$ classes of priorities
that respects all conditions (\ref{cr:bounded} \& \ref{cr:compcs}) of \pref{ssec:hypothesis}.

@@

  However, if $\PHhit{a_0}{b_0}{b_1}$ and $\PHhit{b_0}{a_0}{a_1}$ are replaced by
  $\PHhit{a_0}{a_0}{a_1}$ and $\PHhit{b_0}{b_0}{b_1}$,
  then \pref{th:approxinf} concludes that $c_1$ is reachable from $\ctx$.

\begin{figure}[tp]
  \centering
  \begin{tikzpicture}[aS]
    \node[Aproc] (c1) {$c_1$};
    \node[Aobj,below of=c1] (c01) {$\PHobj{c_0}{c_1}$};
    \node[Asol,below of=c01] (c01s) {};

@@

    (b0) edge (b10) edge (b00)
    (b10) edge (b10s)
    (b00) edge (b00s)
    (b1) edge (b01) edge (b11)
    (b01) edge (b01s)
    (b01s) edge (a0)
    (b11) edge (b11s)
    ;
    \end{tikzpicture}
  \caption{
  \label{fig:sa-livelock}
    The graph of local causality of the PH model in \pref{fig:ph-livelock}.
    Rectangular nodes containing a single process are elements in $\Proc$,
    nodes containing a couple of processes are elements in $\Obj$
    and circle nodes are elements in $\Sol$.
    %The double arrow and the two surrounding nodes represent the only edge in $\Proc \times \Sol$.
    \pref{th:approxinf} is inconclusive on this example as edge $(ab_{11}, \{ a_1, b_1 \}) \in \Proc \times \Sol$ (here represented with a double line) is not coherent (\pref{def:coherent}).
    Indeed, $a_0 \in \Proc$ is a child of $\{ a_1, b_1 \}$, but $a_0 \neq a_1$ (and the same also stands for $b_0$).
  }
\end{figure}
\end{example}
